\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch stable -> A;
    \branch main -> E;
    \HEAD -> main;

    \path [>=stealth', draw=black!50, very thick]
        (5,3.75) node {reference to current branch} edge [->] (HEAD label)
        (6.5,2) node {current branch} edge [->] (main)
        (-5,3) node {another branch}\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \commit 2eecb (2) -> B;
    \branch main -> E;
    \branch stable -> A;
    \olddetachedHEAD -> 2;
    \HEAD -> main;

    \node [cmd] at (0,3.75) {git checkout main};

    \path [line]
        (E) edge [bend left=20] (index)
        (E) edge [bend left=35] (work)
        (old HEAD) edge [dashed, bend left=15] (HEAD label)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \commit 2eecb (2) -> B;
    \branch main -> E;
    \branch stable -> A;
    \olddetachedHEAD -> 2;

    \begin{pgfonlayer}{HEAD}
    \node [branch, double shadow, above right=.4\g of 2, draw=none, fill=none]  
    {};
    \end{pgfonlayer}
    \node [branch, above right=.4\g of 2] (new) {new};
    \path [branch line] (new) edge (2);
    \HEAD -> new;

    \node [cmd] at (-3,3.75) {git checkout -b new};

    \path [line]
        (old HEAD) edge [dashed, bend left=15] (HEAD label)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch main -> E;
    \branch stable -> A;
    \oldHEAD -> main;
    \HEAD -> stable;

    \node [cmd] at (0, 3.75) {git checkout stable};

    \path [line]
        (A) edge [bend right=22] (index)
        (A) edge [bend right=35] (work)
        (old HEAD label) edge [dashed, bend right=10] (HEAD label)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch main -> E;
    \branch stable -> A;
    \oldHEAD -> main;
    \detachedHEAD -> B;

    \node [cmd] at (0, 3.75) {git checkout main\~{}3};

    \path [line]
        (B) edge [bend right=20] (index)
        (B) edge [bend right=40] (work)
        (old HEAD label) edge [dashed, bend right=10] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch main -> E;
    \branch stable -> A;
    \HEAD -> main;

    \node [cmd] at (0, 3.75) {git checkout HEAD\~{} \emph{files}};

    \path [line]
        (D) edge [bend left=20] (index)
        (D) edge [bend left=45] (work)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \newcommit f142b (F) -> E;
    \commit 169a6 (1) -> A;
    \commit 2c33a (2) -> 1;
    \commit 3ba22 (3) -> 2;
    \branch topic -> 3;

    \oldbranch main -> E;
    \oldHEAD -> old main;
    \branch main -> F;
    \HEAD -> main;

    \node [cmd] at (0, 3.75) {git cherry-pick 2c33a};

    \path [line]
        (F) edge [bend left=20] (index)
        (F) edge [bend left=30] (work)
        (old HEAD) edge [dashed, bend left=50] (HEAD)
        (2) edge [loosely dashed, bend right=35] (F)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup

    % trick the code to draw the commit below instead of above
    \pgfkeys{/child count/D=-1}
    \newcommit 4ca87 (4) -> D;

    % this is a special case, so I won't make high level commands for this
    \refbelow [branch] "main" : main -> 4;
    \addHEADbelow [attached HEAD] "HEAD" : HEAD -> main;

    \branch stable -> A;
    \oldbranch main -> E;
    \oldHEAD -> old main;

    \node [cmd] at (0, 3.75) {git commit --amend};

    \path [line]
        (index) edge [bend right=10] (4)
        (old HEAD) edge [dashed, bend left=60] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \newcommit 2eecb (2) -> B;
    \branch main -> E;
    \branch stable -> A;
    \olddetachedHEAD -> B;
    \detachedHEAD -> 2;

    \node [cmd] at (0, 3.75) {git commit};

    % Put a white border underneath the line since it croses over the graph.
    \path [background line]
        ($ (index.north) + (1,0) $) edge [-, bend right=20]
            ($ (2.south east) + (-.09,.01) $);
    \path [line]
        ($ (index.north) + (1,0) $) edge [bend right=20]
            ($ (2.south east) + (-.09,.01) $)
        (old HEAD) edge [dashed, bend left=15] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \newcommit f0cec (F) -> E;
    \oldbranch main -> E;
    \branch main -> F;
    \branch stable -> A;
    \oldHEAD -> old main;
    \HEAD -> main;

    \node [cmd] at (0, 3.75) {git commit};

    \path [line]
        (index) edge [bend right=20] (F)
        (old HEAD) edge [dashed, bend left=50] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \newcommit 1800b (1) -> A;
    \branch main -> E;
    \oldbranch stable -> A;
    \branch stable -> 1;
    \oldHEAD -> old stable;
    \HEAD -> stable;

    \node [cmd] at (0, 3.75) {git commit};

    % Put a white border underneath the line since it croses over the graph.
    \path [background line]
        ($ (index.north) + (-.8,0) $) edge [-, bend right=13]
            ($ (1.south east) + (-.09,.01) $);
    \path [line]
        ($ (index.north) + (-.8,0) $) edge [bend right=13]
            ($ (1.south east) + (-.09,.01) $)
        (old HEAD label) edge [dashed, bend left=10] (HEAD label)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch stable -> A;
    \branch main -> E;
    \HEAD -> main;

    \path [>=stealth', draw=black!50, very thick]
        (5,3.75) node {reference to current branch} edge [->] (HEAD label)
        (6.5,2) node {current branch} edge [->] (main)
        (-5,3) node {another branch} edge [->] (stable)
        (-5,-0.5) node {files to go in next commit} edge [->] (index)
        (-5,-2) node {files that you ``see''} edge [->] (work)
        (5,-1) node [text width=6\g, text badly centered]
          {commit objects, identified by SHA-1 hash}
            edge [->] (E)
            edge [->] (D)
            edge [->] (C)

        (-1,2.25) node {child points to parent} edge [->] ($ (B)!.5!(C) $)
        ;

\end{tikzpicture}
\end{document}

// GoatCounter: https://www.goatcounter.com
// This file (and *only* this file) is released under the ISC license:
// https://opensource.org/licenses/ISC
;(function() {
	'use strict';

	if (window.goatcounter && window.goatcounter.vars)  // Compatibility with very old version; do not use.
		window.goatcounter = window.goatcounter.vars
	else
		window.goatcounter = window.goatcounter || {}

	// Load settings from data-goatcounter-settings.
	var s = document.querySelector('script[data-goatcounter]')
	if (s && s.dataset.goatcounterSettings) {
		try         { var set = JSON.parse(s.dataset.goatcounterSettings) }
		catch (err) { console.error('invalid JSON in data-goatcounter-settings: ' + err) }
		for (var k in set)
			if (['no_onload', 'no_events', 'allow_local', 'allow_frame', 'path', 'title', 'referrer', 'event'].indexOf(k) > -1)
				window.goatcounter[k] = set[k]
	}

	var enc = encodeURIComponent

	// Get all data we're going to send off to the counter endpoint.
	var get_data = function(vars) {
		var data = {
			p: (vars.path     === undefined ? goatcounter.path     : vars.path),
			r: (vars.referrer === undefined ? goatcounter.referrer : vars.referrer),
			t: (vars.title    === undefined ? goatcounter.title    : vars.title),
			e: !!(vars.event || goatcounter.event),
			s: [window.screen.width, window.screen.height, (window.devicePixelRatio || 1)],
			b: is_bot(),
			q: location.search,
		}

		var rcb, pcb, tcb  // Save callbacks to apply later.
		if (typeof(data.r) === 'function') rcb = data.r
		if (typeof(data.t) === 'function') tcb = data.t
		if (typeof(data.p) === 'function') pcb = data.p

		if (is_empty(data.r)) data.r = document.referrer
		if (is_empty(data.t)) data.t = document.title
		if (is_empty(data.p)) data.p = get_path()

		if (rcb) data.r = rcb(data.r)
		if (tcb) data.t = tcb(data.t)
		if (pcb) data.p = pcb(data.p)
		return data
	}

	// Check if a value is "empty" for the purpose of get_data().
	var is_empty = function(v) { return v === null || v === undefined || typeof(v) === 'function' }

	// See if this looks like a bot; there is some additional filtering on the
	// backend, but these properties can't be fetched from there.
	var is_bot = function() {
		// Headless browsers are probably a bot.
		var w = window, d = document
		if (w.callPhantom || w._phantom || w.phantom)
			return 150
		if (w.__nightmare)
			return 151
		if (d.__selenium_unwrapped || d.__webdriver_evaluate || d.__driver_evaluate)
			return 152
		if (navigator.webdriver)
			return 153
		return 0
	}

	// Object to urlencoded string, starting with a ?.
	var urlencode = function(obj) {
		var p = []
		for (var k in obj)
			if (obj[k] !== '' && obj[k] !== null && obj[k] !== undefined && obj[k] !== false)
				p.push(enc(k) + '=' + enc(obj[k]))
		return '?' + p.join('&')
	}

	// Show a warning in the console.
	var warn = function(msg) {
		if (console && 'warn' in console)
			console.warn('goatcounter: ' + msg)
	}

	// Get the endpoint to send requests to.
	var get_endpoint = function() {
		var s = document.querySelector('script[data-goatcounter]')
		if (s && s.dataset.goatcounter)
			return s.dataset.goatcounter
		return (goatcounter.endpoint || window.counter)  // counter is for compat; don't use.
	}

	// Get current path.
	var get_path = function() {
		var loc = location,
			c = document.querySelector('link[rel="canonical"][href]')
		if (c) {  // May be relative or point to different domain.
			var a = document.createElement('a')
			a.href = c.href
			if (a.hostname.replace(/^www\./, '') === location.hostname.replace(/^www\./, ''))
				loc = a
		}
		return (loc.pathname + loc.search) || '/'
	}

	// Run function after DOM is loaded.
	var on_load = function(f) {
		if (document.body === null)
			document.addEventListener('DOMContentLoaded', function() { f() }, false)
		else
			f()
	}

	// Filter some requests that we (probably) don't want to count.
	goatcounter.filter = function() {
		if ('visibilityState' in document && document.visibilityState === 'prerender')
			return 'visibilityState'
		if (!goatcounter.allow_frame && location !== parent.location)
			return 'frame'
		if (!goatcounter.allow_local && location.hostname.match(/(localhost$|^127\.|^10\.|^172\.(1[6-9]|2[0-9]|3[0-1])\.|^192\.168\.|^0\.0\.0\.0$)/))
			return 'localhost'
		if (!goatcounter.allow_local && location.protocol === 'file:')
			return 'localfile'
		if (localStorage && localStorage.getItem('skipgc') === 't')
			return 'disabled with #toggle-goatcounter'
		return false
	}

	// Get URL to send to GoatCounter.
	window.goatcounter.url = function(vars) {
		var data = get_data(vars || {})
		if (data.p === null)  // null from user callback.
			return
		data.rnd = Math.random().toString(36).substr(2, 5)  // Browsers don't always listen to Cache-Control.

		var endpoint = get_endpoint()
		if (!endpoint)
			return warn('no endpoint found')

		return endpoint + urlencode(data)
	}

	// Count a hit.
	window.goatcounter.count = function(vars) {
		var f = goatcounter.filter()
		if (f)
			return warn('not counting because of: ' + f)

		var url = goatcounter.url(vars)
		if (!url)
			return warn('not counting because path callback returned null')

		var img = document.createElement('img')
		img.src = url
		img.style.position = 'absolute'  // Affect layout less.
		img.style.bottom = '0px'
		img.style.width = '1px'
		img.style.height = '1px'
		img.loading = 'eager'
		img.setAttribute('alt', '')
		img.setAttribute('aria-hidden', 'true')

		var rm = function() { if (img && img.parentNode) img.parentNode.removeChild(img) }
		img.addEventListener('load', rm, false)
		document.body.appendChild(img)
	}

	// Get a query parameter.
	window.goatcounter.get_query = function(name) {
		var s = location.search.substr(1).split('&')
		for (var i = 0; i < s.length; i++)
			if (s[i].toLowerCase().indexOf(name.toLowerCase() + '=') === 0)
				return s[i].substr(name.length + 1)
	}

	// Track click events.
	window.goatcounter.bind_events = function() {
		if (!document.querySelectorAll)  // Just in case someone uses an ancient browser.
			return

		var send = function(elem) {
			return function() {
				goatcounter.count({
					event:    true,
					path:     (elem.dataset.goatcounterClick || elem.name || elem.id || ''),
					title:    (elem.dataset.goatcounterTitle || elem.title || (elem.innerHTML || '').substr(0, 200) || ''),
					referrer: (elem.dataset.goatcounterReferrer || elem.dataset.goatcounterReferral || ''),
				})
			}
		}

		Array.prototype.slice.call(document.querySelectorAll("*[data-goatcounter-click]")).forEach(function(elem) {
			if (elem.dataset.goatcounterBound)
				return
			var f = send(elem)
			elem.addEventListener('click', f, false)
			elem.addEventListener('auxclick', f, false)  // Middle click.
			elem.dataset.goatcounterBound = 'true'
		})
	}

	// Add a "visitor counter" frame or image.
	window.goatcounter.visit_count = function(opt) {
		on_load(function() {
			opt        = opt        || {}
			opt.type   = opt.type   || 'html'
			opt.append = opt.append || 'body'
			opt.path   = opt.path   || get_path()
			opt.attr   = opt.attr   || {width: '200', height: (opt.no_branding ? '60' : '80')}

			opt.attr['src'] = get_endpoint() + 'er/' + enc(opt.path) + '.' + enc(opt.type) + '?'
			if (opt.no_branding) opt.attr['src'] += '&no_branding=1'
			if (opt.style)       opt.attr['src'] += '&style=' + enc(opt.style)
			if (opt.start)       opt.attr['src'] += '&start=' + enc(opt.start)
			if (opt.end)         opt.attr['src'] += '&end='   + enc(opt.end)

			var tag = {png: 'img', svg: 'img', html: 'iframe'}[opt.type]
			if (!tag)
				return warn('visit_count: unknown type: ' + opt.type)

			if (opt.type === 'html') {
				opt.attr['frameborder'] = '0'
				opt.attr['scrolling']   = 'no'
			}

			var d = document.createElement(tag)
			for (var k in opt.attr)
				d.setAttribute(k, opt.attr[k])

			var p = document.querySelector(opt.append)
			if (!p)
				return warn('visit_count: append not found: ' + opt.append)
			p.appendChild(d)
		})
	}

	// Make it easy to skip your own views.
	if (location.hash === '#toggle-goatcounter') {
		if (localStorage.getItem('skipgc') === 't') {
			localStorage.removeItem('skipgc', 't')
			alert('GoatCounter tracking is now ENABLED in this browser.')
		}
		else {
			localStorage.setItem('skipgc', 't')
			alert('GoatCounter tracking is now DISABLED in this browser until ' + location + ' is loaded again.')
		}
	}

	if (!goatcounter.no_onload)
		on_load(function() {
			// 1. Page is visible, count request.
			// 2. Page is not yet visible; wait until it switches to 'visible' and count.
			// See #487
			if (!('visibilityState' in document) || document.visibilityState === 'visible')
				goatcounter.count()
			else {
				var f = function(e) {
					if (document.visibilityState !== 'visible')
						return
					document.removeEventListener('visibilitychange', f)
					goatcounter.count()
				}
				document.addEventListener('visibilitychange', f)
			}

			if (!goatcounter.no_events)
				goatcounter.bind_events()
		})
})();

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \normalcommits
    \indexnode[2,-3]
    \worknode[-2,-3]
    \commit 2eecb (2) -> B;
    \commit 33104 (3) -> 2;
    \branch other -> 3;

    % draw the old branch manually with a long line
    \node [old branch, above=1 of E] (old main) {main};
    \path [old branch line] (old main) edge (E);
    \node [cancel ref, above=.2\g of E, anchor=center] {};
    \oldHEAD -> old main;

    \newcommit f8bc5 (F) -> E;
    \branch main -> F;
    \HEAD -> main;
    \path [background line, bend right=15] (F) edge[-] (3);
    \path [commit line, bend right=15] (F) edge (3);

    \node [cmd] at (0, 3.75) {git merge other};

    \node [inner sep=8\gLine] (merge) at (0,-1) {3-way merge};

    \path [background line]
        (3) edge [-, bend right=15] (merge)
        ;
    \path [line]
        (3) edge [bend right=15] (merge)
        (B) edge [bend right=37] (merge)
        (E) edge [bend left=20] (merge)
        (merge) edge [bend right=10] (index)
        (merge) edge [bend left=10] (work)
        (index) edge [bend right=35] node [near start] {(if no conflicts)} (F)
        (old HEAD label) edge [dashed, bend left=35] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \refbelow [branch] "main" : main -> E;
    \oldbranch stable -> A;
    \branch stable -> E;
    \oldHEAD -> old stable;
    \HEAD -> stable;

    \node [cmd] at (0, 3.75) {git merge main};

    \path [line]
        (E) edge [bend right=5] (index.north east)
        (E) edge [bend right=15] (work.north east)
        (old HEAD) edge [dashed, bend left=10] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \indexnode
    \worknode
    \commitTerminal cT at (-6,.75);
    \commit a47c3 (A) -> cT;
    \commit b325c (B) -> A;
    \commit c10b9 (C) -> B;
    \commit da985 (D) -> C;
    \newcommit e57cf (E) -> D;
    \newcommit f7e63 (F) -> E;
    \commit 169a6 (1) -> A;
    \commit 2c33a (2) -> 1;

    \oldbranch topic -> 2;
    \oldHEAD -> old topic;
    \branch main -> D;
    \branch topic -> F;
    \HEAD -> topic;

    \node [cmd,right] at (1, 3.75) {git rebase main};

    \path [line]
        (F) edge [bend left=20] (index)
        (F) edge [bend left=30] (work)
        (old HEAD label) edge [dashed, bend left=10] (HEAD label)
        (1) edge [loosely dashed, bend right=35] (E)
        (2) edge [loosely dashed, bend left=30] (F)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \indexnode
    \worknode
    \commitTerminal cT at (-6,.75);
    \commit a47c3 (A) -> cT;
    \commit b325c (B) -> A;
    \commit c10b9 (C) -> B;
    \commit da985 (D) -> C;
    \newcommit e918c (E) -> D;
    \commit 169a6 (1) -> A;
    \commit 2c33a (2) -> 1;

    \oldbranch topic -> 2;
    \oldHEAD -> old topic;
    \branch main -> D;
    \branch topic -> E;
    \HEAD -> topic;

    \node [cmd,right] at (1, 3.75) {git rebase --onto main 169a6};

    \path [line]
        (E) edge [bend left=20] (index)
        (E) edge [bend left=30] (work)
        (old HEAD label) edge [dashed, bend left=10] (HEAD label)
        (2) edge [loosely dashed, bend right=40] (E)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch main -> E;
    \branch stable -> A;
    \HEAD -> main;

    \node [cmd] (cmd1) at (0, 3.75) {git reset};

    \path [line, auto=left]
        (E) edge [bend left=20] (index)
        (E) edge [bend left=30] node {(if \texttt{--hard})} (work)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch stable -> A;
    \oldbranch main -> E;
    \branch main -> B;
    \oldHEAD -> old main;
    \HEAD -> main;

    \node [cmd] at (0, 3.75) {git reset HEAD\~{}3};

    \path [line, auto=left]
        (B) edge [bend right=20] node [near end]
          {(if not \texttt{--soft})} (index)
        (B) edge [bend right=40] node [swap] {(if \texttt{--hard})} (work)
        (old HEAD) edge [dashed, bend right=15] (HEAD)
        ;

\end{tikzpicture}
\end{document}

\input{common.tex}
\begin{document}
\begin{tikzpicture}[main]
    \boundingbox
    \usualsetup
    \branch main -> E;
    \branch stable -> A;
    \HEAD -> main;

    \node [cmd] (cmd1) at (0, 3.75) {git reset -- \emph{files}};

    \path [line]
        (E) edge [bend left=20] (index)
        ;

\end{tikzpicture}
\end{document}

html{
    background: #FAFAFA;
}

body{
    font-family: sans-serif;
    margin: 0 auto;
    width: 70%;
    padding: 20px 0px;
    background: white;
    box-shadow: 0 1px 5px rgba(0, 0, 0, 0.25);
    color: rgba(0,0,0,0.7);
}

@media handheld, screen and (max-width: 995px){
    body{
        width: 100%;
    }
}

h1, h2, h3{
    color: rgba(0,0,0,0.8);
    margin-left: 20px;
    margin-right: 20px;
}

h1{font-size: 4rem;}
h2{font-size: 2rem;}
h3{font-size: 1.2rem;}

a, a:visited{
    text-decoration: none;
    color: #f05033;
    font-size: 1rem;
}


p, div, ol, ul, pre, strong{
    margin-left: 20px;
    margin-right: 20px;
}

hr{
    color: #212121;
    height: 1px;
    background: #BDBDBD;
}


.center {
    text-align: center;
}
#link-to-png, #link-to-svg {
    font-style: italic; display: none;
}
ol ol {
    list-style-type: lower-alpha;
}
#language-box {
    position: absolute;
    top: 2px;
    font-family: sans-serif;
    list-style: none;
    margin: 0;
    padding: 0;
    text-align: center;
}
#language-box ul {
    display: inline;
    list-style: none;
    margin: 0 0 0 -0.5em;
    padding: 0.5em;
    width: 100%;
}
#language-box ul li {
    padding: .2ex 0;
    display: inline;
}
#language-box ul li.selected {
    display: none;
}
@media print {
    #language-box {
        display: none;
    }
    body{
        width: 100%;
    }
}
pre {
  margin-left: 2em;
}

// Webkit browsers can't zoom properly with object tags.
if (navigator.userAgent.indexOf("AppleWebKit") > -1) {
  replacePNG = function(img, src) {
    var h = img.height, w = img.width;
    img.src = src;
    img.height = h;
    img.width = w;
    return 0;
  }
} else {
  replacePNG = function(img, src) {
    var p = img.parentNode;
    var obj = document.createElement('object');
    obj.type = 'image/svg+xml';
    obj.data = src;
    obj.width = img.width;
    obj.height = img.height;
    p.appendChild(obj);
    p.removeChild(img);
    return -1;
  }
}
var svg_disabled = window.location.search.indexOf("no-svg") > 0;
// Replace all the PNGs with SVGs on browsers that support them.
function replace_all_PNGs() {
  var hasSVG = document.implementation.hasFeature("http://www.w3.org/TR/SVG11/feature#BasicStructure", "1.1");
  if (hasSVG) {
    if (svg_disabled) {
      document.getElementById('link-to-svg').style.display = 'block';
      return;
    }
    var images = document.getElementsByTagName('img');
    for (var i = 0; i < images.length; i++) {
      var img = images[i];
      var src = img.src.match(/^(.*\.svg)\.png$/)
      if (src)
        i += replacePNG(img, src[1]);
    }
    document.getElementById('link-to-png').style.display = 'block';
  }
}

// enable Google Analytics
var _gaq = _gaq || [];
_gaq.push(['_setAccount', 'UA-13167645-1']);
_gaq.push(['_trackPageview']);
(function() {
  var ga = document.createElement('script'); ga.type = 'text/javascript'; ga.async = true;
  ga.src = ('https:' == document.location.protocol ? 'https://ssl' : 'http://www') + '.google-analytics.com/ga.js';
  var s = document.getElementsByTagName('script')[0]; s.parentNode.insertBefore(ga, s);
})();
 edge [->] (stable)
        (-5,-0.5) node {files to go in next commit} edge [->] (index)
        (-5,-2) node {files that you ``see''} edge [->] (work)
        (5,-1) node [text width=6\g, text badly centered]
          {commit objects, identified by SHA-1 hash}
            edge [->] (E)
            edge [->] (D)
            edge [->] (C)

        (-1,2.25) node {child points to parent} edge [->] ($ (B)!.5!(C) $)
        ;

\end{tikzpicture}
\end{document}
